IARC Technical Paper

### 2017-05-31 IARC_Paper/Paper.tex
Some content changes. Possibily final version.

\section{Conclusion}
We still have quite a ways to go before we can consider ourselves competitive. Due to the fact that we started our organization in 2017, we have come a long way and learned a lot, yet we plan to continue work to beat this mission as quick as possible. Hopefully we do well at Georgia Tech!

>>>>

\section{Conclusion}
Last year, Texas Aerial Robotics was a mere idea in the minds of the student engineers participating today. Because of the incredible drive of the founding members, TAR will have a solid showing at the competition in July. Not only has the team risen to the engineering challenge, they have built a sustainable team that is rooted in the engineering process and will allow TAR to expand in the coming years. All of the current members will be returning next year to further develop their knowledge and understanding of engineering and technology as well as spread their vision of drone technology to other students at UT Austin.
